Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-07-01 supplement/05_calibration_data.Rmd

In all, we aim to keep three versions of the data: (1) `data_raw`, the entirely unprocessed data, (2) `data`, the working version, and (3) `data_unproc`, data that has been partially processed, but which is one step behind `data`. This allows us to better illustrate the pre-processing steps, and prevents us from irreversibly modifying our data --- at best, we would have to re-run many pre-processing steps, and at worse, we might overwrite the data on disk.

>>>>

In all, we aim to keep three versions of the data: (1) `data_raw`, the entirely unprocessed data, (2) `data`, the working version, and (3) `data_unproc`, data that has been partially processed, but which is one step behind `data`. This allows us to better illustrate the pre-processing steps, and prevents us from irreversibly modifying our data --- at best, we would have to re-run many pre-processing steps, and at worst, we might overwrite the original data on disk.
